Digital Addiction

### 2024-02-15 output/paper.qmd
paper
try import data into paper

@@

>>>>

#install.packages("tidyverse")
#install.packages("haven")
#install.packages("readxl")
#install.packages("janitor")
#install.packages("ggpubr")

library(tidyverse)
library(haven)
library(readxl)
library(janitor)
library(ggpubr)

setwd("..")
#### Import Data ####
#### Explore ####
dinesafe_program_clean <-
  read_csv(
   here::here("scripts/02_data_cleaning.R"),
    show_col_types = FALSE
  )

@@

# Result

# Discuss

# Reference
